---
title: "College Admission Prediction"
author: "Deo Ivan Mareza"
date: "`14 Feburary 2020`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# INTRODUCTION

In this exercise, we want to see the chance of someone getting into a university of their choice using linear regression method.


<font size = "2">
The data is kindly provided by : Mohan S Acharya, Asfia Armaan, Aneeta S Antony : A Comparison of Regression Models for Prediction of Graduate Admissions, IEEE International Conference on Computational Intelligence in Data Science 2019
</font>



# DATA PREPARATION


Library packages that we're using
```{r,warning=FALSE, results='hide',message=FALSE}

library(tidyverse)
library(GGally)
library(MLmetrics)
library(car)
library(lmtest)

```

Reading the data
```{r,warning=FALSE, results='hide',message=FALSE}

admission <- read_csv("data_input/Admission_Predict_Ver1.1.csv")

```

Checking the data
```{r}

head(admission)

```



